False Positive Probabilities for all Kepler Objects of Interest: \\ \nvalnew\ newly validated planets and \nfpnew\ likely false positives

### 2015-07-22 ms.tex
more writing

\usepackage{natbib}
\usepackage{acronym}
\bibliographystyle{apj}

@@

\newcommand{\ntotal}{5500}
\newcommand{\nfail}{1000}
\newcommand{\nval}{1500}
\newcommand{\nvalnew}{1000}
\newcommand{\nfp}{500}
\newcommand{\nfpnew}{200}
\newcommand{\kepler}{\textit{Kepler}}
\newcommand{\vespa}{\texttt{vespa}}
\newcommand{\isochrones}{\texttt{isochrones}}

@@

\acrodef{fpp}[FPP]{false positive probability}
\acrodef{koi}[KOI]{\kepler\ Object of Interest}
\acrodefplural{koi}[KOIs]{\kepler\ Objects of Interest}
\acrodef{nexsci}[NExScI]{NASA Exoplanet Science Institute}

@@

In this work, we apply the fully automated \ac{fpp}-computing
procedure described in \citet{Morton:2012}
\citepalias[][hereafter]{Morton:2012} to all \acp{koi} listed in the
``cumulative'' \kepler\ data table at the \ac{nexsci} Exoplanet
Archive.  While we refer the reader to \citetalias{Morton:2012} for a
detailed description of the method, we outline it briefly here, noting
especially the differences between the current implementation and
\citetalias{Morton:2012}.  The procedure as implemented in this work
is now publicly available in the Python module
\vespa\footnote{\url{https://github.com/timothydmorton/vespa}}.

The basic goal of \vespa\ is to assign probabilities to different
astrophysical hypotheses that might describe a transiting planet
candidate signal.  If $\{H_i\}$ is the set of all considered
hypotheses, the probability for any given model $i$ is
\begin{equation}
  \label{eq:prob}
  \mathrm{Pr}(H_i) = \frac{\mathcal L_i \pi_i}{\displaystyle \sum_j \mathcal L_j \pi_j}
\end{equation}
where $\mathcal L_i$ and $\pi_i$ are the ``likelihood'' and ``prior''
factors for each hypothesis.

eclipse signals as simple
trapezoidal

The first step in calculating the \ac{fpp} of a transit signal is to
determine the physical properties of the signal host star.  To
accomplish this, we use the Python module \isochrones
\citep{isochrones}, which fits a stellar model grid of choice to a set
of observed properties of a given star.

In \citetalias{Morton:2012},

@@

>>>>

\usepackage{natbib}
\usepackage{acronym}
\usepackage{amssymb,amsmath}

\bibliographystyle{apj}

@@

\newcommand{\ntotal}{5500}
\newcommand{\nfail}{1000}
\newcommand{\nval}{1500}
\newcommand{\nvalnew}{1000}
\newcommand{\nfp}{500}
\newcommand{\nfpnew}{200}
\newcommand{\kepler}{\textit{Kepler}}
\newcommand{\vespa}{\texttt{vespa}}
\newcommand{\isochrones}{\texttt{isochrones}}
\newcommand{\bvec}[1]{{\ensuremath{\boldsymbol{#1}}}}

@@

\acrodef{fpp}[FPP]{false positive probability}
\acrodef{koi}[KOI]{\kepler\ Object of Interest}
\acrodefplural{koi}[KOIs]{\kepler\ Objects of Interest}
\acrodef{nexsci}[NExScI]{NASA Exoplanet Science Institute}
\acrodef{mcmc}[MCMC]{Markov Chain Monte Carlo}
\acrodef{trilegal}[TRILEGAL]{TRIdimensional modeL of thE GALaxy}

@@

In this work, we apply the fully automated \ac{fpp}-computing
procedure described in \citet[][hereafter
  \citetalias{Morton:2012}]{Morton:2012} to all \acp{koi} listed in
the ``cumulative'' \kepler\ data table at the \ac{nexsci} Exoplanet
Archive.  While we refer the reader to \citetalias{Morton:2012} for a
detailed description of the method, we outline it briefly in this
section.  The procedure as implemented here is now publicly available
in the Python module
\vespa\footnote{\url{https://github.com/timothydmorton/vespa}}.

@@

The basic idea of \vespa\ is to assign probabilities to different
astrophysical hypotheses that might describe a transiting planet
candidate signal.  If $\{H_i\}$ is the set of all considered
hypotheses, the probability for any given model $i$ is
\begin{equation}
  \label{eq:prob}
  \mathrm{Pr}\left(H_i\right) = \frac{\pi_i \mathcal
    L_i}{\displaystyle \sum_j \pi_j \mathcal L_j},
\end{equation}
where $\pi_i$ is the ``hypothesis prior'' and $\mathcal L_i$ is the
``hypothesis likelihood'' (also known as ``evidence'' or
``marginalized likelihood'').  The prior represents how intrinsically
probable the hypothesized scenario is to exist, and the likelihood
represents how closely the shape of the observed transit signal
matches with the expected shape of a signal produced by the
hypothesis.

\vespa\ models an eclipse signal as a simple trapezoid, parametrized
by depth $\delta$, total duration $T$, and shape parameter $T / \tau$,
where $\tau$ is the ``ingress/egress'' duration (such that a
completely V-shaped transit has $T/\tau = 2$).  For the transit signal
being evaluated, the joint posterior probability density function
(PDF) of these shape parameters is sampled with \ac{mcmc}, using the
\texttt{emcee} sampler \citep{emcee}.  This allows the likelihood for
each hypothesis to be determined by simulating a physically realistic
population of the hypothesized astrophysical scenario and using this
population to define the PDF for the trapezoidal parameters under the
hypothesis.  The likelihood is then
\begin{equation}
  \label{eq:lhood}
  \mathcal L_i = \displaystyle \int p_\mathrm{sig}\left(\bvec{\theta}\right)
                                    p_i\left(\bvec{\theta}\right)\,d\bvec{\theta},
\end{equation}
where $\bvec{\theta}$ is the vector of trapezoidal shape parameters,
$p_\mathrm{sig}$ is the posterior PDF of the signal, and $p_i$ is the
PDF for the parameters under hypothesis $i$.

Observational constraints are incorporated in two different ways.
First, photometric (or spectroscopic/asteroseismic) measurements of
the target star are folded into the population simulations of each
hypothesis (see \S\ref{sec:methods:stellar}).  All other constraints are
applied to narrow down which simulated instances of each scenario may
be counted in the final prior and likelihood evalulations; for example,
only blended eclipsing binaries with secondary eclipse depths
shallower than the observed limits are allowed.

The steps \vespa\ takes to calculate the \ac{fpp} of a transit signal
are thus as follows:
\begin{enumerate}
\item Fit trapezoid model to observed transit signal using \ac{mcmc}.
\item Generate population simulations for each hypothesis scenario
  being considered (conditioned on available observations of the
  target star; see \S\ref{sec:methods:stellar}).
\item Fit each simulated eclipse in each scenario with a trapezoid
  model (using least-squares optimization).
\item Evaluate priors and likelihoods for each hypothesis, taking into
  account all available observational constraints, in order to
  calculate the \ac{fpp}.
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%

The most substantial difference between the current implementation of
\vespa\ and the procedure documented in \citetalias{Morton:2012} is
how stellar properties are treated.  Previously, either the target
star's mass and radius were explicitly provided, or they were randomly
generated according to the stellar population expected along the line
of sight by \ac{trilegal}, but constrained to agree with some observed
color(s) of the star (e.g. $J-K$), to within some specified tolerance.
This strategy was used both to generate the host stars for the
transiting planet model and the binary and triple stars for the EB and
HEB false positive models.

The new method now used by \vespa\ to fold in observational
constraints on the host star debuted in \citet{Montet:2015} (and is
explained there in more detail).  Instead of randomly generating stars
(or binary or triple systems of stars) from a predefined distribution and
culling them to agree with observed colors, \emph{all} available
constraints on the target star are used to condition a direct fit of
either a single-, binary-, or triple-star model to the Dartmouth grid
of stellar models.  This fit is done using \texttt{MultiNest}, via the
\isochrones\footnote{\url{https://github.com/timothydmorton/isochrones}}
Python module.  Monte Carlo samples of stellar properties for the
population simulations are then drawn directly from these posterior
samples.

As a result, a by-product of the \vespa\ \ac{fpp} calculation is full
posterior samples of the physical properties of the star, modeled as a
single, binary, or triple system.  Parameters directly fitted for in
this process are stellar mass, age, [Fe/H], $A_V$ extinction, and
distance.  For binary and triple fits, secondary and/or tertiary mass
parameters are added, with all other parameters assumed to be the same
among all components.  Photometric observations upon which these fits
are conditioned are assumed to be the sum of all components.  If
spectroscopic and/or asteroseismic measurements are used (e.g.,
constraints on effective temperature or stellar surface gravity), they
are assumed to relate to only the primary star.  Priors used in these
fits are listed in Table \ref{table:priors}.  Posterior chains of all
other stellar parameters of interest (e.g., temperature, surface
gravity, radius, etc.) are derived from the chains of fitting
parameters by evaluting the stellar models.

\begin{deluxetable}{cc}
\tablewidth{0pt}
\tabletypesize{\scriptsize}
\tablecaption{Priors used in stellar fits}
\tablehead{
\colhead{Parameter} &
\colhead{Prior}}
\startdata
Primary mass $M$ & $\propto M^{-2.35}$ \\
Age {[}Gyr{]} & $\mathcal U(1,15) $\\
{[}Fe/H{]} & $\frac{0.8}{0.15} \mathcal N(0.016, 0.15) + \frac{0.2}{0.22} \mathcal N(-0.15, 0.22)$ \\
$A_V$ {[}mag{]} & $\mathcal U(0, A_{V, \mathrm{max}})$ \\
Distance d & $\propto d^2$ 
\enddata
\label{table:priors}
\end{deluxetable}
